SubsidyExplorer - Step 0: Data Wrangling

### 2020-03-26 papers/paper-1/paper_1_figures.Rmd
and paper figures again

# Path to binned effort data file
effort_dat_binned_path <- here::here("results", "02-vessel-list", "effort_binned_good_fishing_vessels_2018_raw.csv")

@@

# Total subsidies (grid)
subsidy_intensity_tot_grid_l <- MapMaker(data = subsidy_intensity_binned,
                                         res = "grid",
                                         x = "lon_bin_center",
                                         y = "lat_bin_center",
                                         fill = "tot_subs_KWh",
                                         fill_name = subs_fill_label,
                                         fill_breaks = tot_subs_fill_breaks,
                                         fill_limits = tot_subs_fill_limits,
                                         fill_labels = tot_subs_fill_labels,
                                         land_sf = world_land,
                                         plot_labels = c("A) Median", "B) Mean", "C) Weighted Mean"),
                                         file_name = "subsidy_intensity_tot_grid_map",
                                         file_dir = results_dir)

@@

```{r, fig.width=4, fig.height=7}
# Total subsidies (region)
subsidy_intensity_tot_region_l <- MapMaker(data = subsidy_intensity_region,
                                         res = "region",
                                         x = "lon_bin_center",
                                         y = "lat_bin_center",
                                         fill = "tot_subs_KWh",
                                         fill_name = subs_fill_label,
                                         fill_breaks = tot_subs_fill_breaks,
                                         fill_limits = tot_subs_fill_limits,
                                         fill_labels = tot_subs_fill_labels,
                                         land_sf = world_land,
                                         region_sf = fao_regions,
                                         plot_labels = c("A) Median", "B) Mean", "C) Weighted Mean"),
                                         file_name = "subsidy_intensity_tot_region_map",
                                         file_dir = results_dir)

@@

# Total subsidies (grid)
subsidy_intensity_B_grid_l <- MapMaker(data = subsidy_intensity_binned,
                                         res = "grid",
                                         x = "lon_bin_center",
                                         y = "lat_bin_center",
                                         fill = "B_subs_KWh",
                                         fill_name = subs_fill_label,
                                         fill_breaks = B_subs_fill_breaks,
                                         fill_limits = B_subs_fill_limits,
                                         fill_labels = B_subs_fill_labels,
                                         land_sf = world_land,
                                         plot_labels = c("A) Median", "B) Mean", "C) Weighted Mean"),
                                         file_name = "subsidy_intensity_B_grid_map",
                                         file_dir = results_dir)

@@

```{r, fig.width=4, fig.height=7}
# Total subsidies (region)
subsidy_intensity_B_region_l <- MapMaker(data = subsidy_intensity_region,
                                         res = "region",
                                         x = "lon_bin_center",
                                         y = "lat_bin_center",
                                         fill = "B_subs_KWh",
                                         fill_name = subs_fill_label,
                                         fill_breaks = B_subs_fill_breaks,
                                         fill_limits = B_subs_fill_limits,
                                         fill_labels = B_subs_fill_labels,
                                         land_sf = world_land,
                                         region_sf = fao_regions,
                                         plot_labels = c("A) Median", "B) Mean", "C) Weighted Mean"),
                                         file_name = "subsidy_intensity_B_region_map",
                                         file_dir = results_dir)

@@

# Total subsidies (grid)
subsidy_intensity_BC_grid_l <- MapMaker(data = subsidy_intensity_binned,
                                         res = "grid",
                                         x = "lon_bin_center",
                                         y = "lat_bin_center",
                                         fill = "BC_subs_KWh",
                                         fill_name = subs_fill_label,
                                         fill_breaks = BC_subs_fill_breaks,
                                         fill_limits = BC_subs_fill_limits,
                                         fill_labels = BC_subs_fill_labels,
                                         land_sf = world_land,
                                         plot_labels = c("A) Median", "B) Mean", "C) Weighted Mean"),
                                         file_name = "subsidy_intensity_BC_grid_map",
                                         file_dir = results_dir)

@@

```{r, fig.width=4, fig.height=7}
# Total subsidies (region)
subsidy_intensity_BC_region_l <- MapMaker(data = subsidy_intensity_region,
                                         res = "region",
                                         x = "lon_bin_center",
                                         y = "lat_bin_center",
                                         fill = "BC_subs_KWh",
                                         fill_name = subs_fill_label,
                                         fill_breaks = BC_subs_fill_breaks,
                                         fill_limits = BC_subs_fill_limits,
                                         fill_labels = BC_subs_fill_labels,
                                         land_sf = world_land,
                                         region_sf = fao_regions,
                                         plot_labels = c("A) Median", "B) Mean", "C) Weighted Mean"),
                                         file_name = "subsidy_intensity_BC_region_map",
                                         file_dir = results_dir)

@@

```{r, fig.width=4, fig.height=7}
# Fmsy (region)
F_Fmsy_region_l <- MapMaker(data = upsides_region,
                            res = "region",
                            fill = "fv_fmsy",
                            fill_name = "F/Fmsy",
                            fill_breaks = seq(0,3, by = 0.75),
                            fill_limits = c(0, 3),
                            fill_labels = c("0", "0.75", "1.5", "2.25", "\u2265 3"),
                            land_sf = world_land,
                            region_sf = fao_regions,
                            plot_labels = c("A) Median", "B) Mean", "C) Weighted Mean"),
                            file_name = "F_Fmsy_region_map",
                            file_dir = results_dir)

@@

```{r, fig.width=4, fig.height=7}
# B/Bmsy (region)
B_Bmsy_region_l <- MapMaker(data = upsides_region,
                            res = "region",
                            fill = "bv_bmsy",
                            fill_name = "B/Bmsy",
                            fill_breaks = seq(0,2, by = 0.5),
                            fill_limits = c(0, 2),
                            fill_labels = c("0", "0.5", "1", "1.5", "\u2265 2"),
                            land_sf = world_land,
                            region_sf = fao_regions,
                            plot_labels = c("A) Median", "B) Mean", "C) Weighted Mean"),
                            file_name = "B_Bmsy_region_map",
                            file_dir = results_dir)

@@

```{r}
# Set some plot scales
subs_x <- c(0,2.5)
f_y <- c(0,3)
effort_fill_lim <- c(0,7.5e9)
effort_fill_breaks <- seq(0,7.5e9, length.out = 5)
effort_fill_labels <- format(seq(0,7.5e9, length.out = 5)/1e9, scientific = F, digits = 2)

@@

```{r}
w_mean_fuel_subs_vs_F_Fmsy_l <- MapMaker(data = subsidy_intensity_upsides_region,
                                        res = "corr",
                                        x = "fuel_subs_KWh_w_mean",
                                        x_name = paste0("Weighted Mean Subsidy Intensity ($/KWh)"),
                                        x_limits = subs_x,
                                        y = "fv_fmsy",
                                        y_name = f_label,
                                        y_limits = f_y,
                                        fill = "fishing_KWh_lat_lon_sum",
                                        fill_name = effort_label,
                                        fill_limits = effort_fill_lim,
                                        fill_breaks = effort_fill_breaks,
                                        fill_labels = effort_fill_labels,
                                        file_name = "w_mean_fuel_subs_vs_F_Fmsy_plot",
                                        file_dir = results_dir)

@@

## Figure 1

```{r}
top_row <- #plot_grid(

  #get_legend(subsidy_intensity_BC_grid_l[["w_mean"]]),

  plot_grid(subsidy_intensity_BC_region_l[["w_mean"]],
            F_Fmsy_region_l[["median"]],
            nrow = 1,
            label_x = 0,
            labels = c("A)", "B)"))

  # ncol = 1,
  # rel_heights = c(0.1, 1)

#)

Figure1 <- plot_grid(top_row,
                     w_mean_BC_subs_vs_F_Fmsy_l[["median"]],
                     nrow = 2,
                     labels = c("", "C)"),
                     label_y = 1.05)

>>>>

# Path to binned effort data file
effort_dat_binned_path <- here::here("results", "02-vessel-list", "effort_1x1_good_fishing_vessels_2018_raw.csv")

@@

# Total subsidies (grid)
subsidy_intensity_tot_grid_l <- MapMaker(data = subsidy_intensity_binned,
                                         res = "grid",
                                         x = "lon_bin_center",
                                         y = "lat_bin_center",
                                         fill = "tot_subs_KWh",
                                         fill_name = subs_fill_label,
                                         fill_breaks = tot_subs_fill_breaks,
                                         fill_limits = tot_subs_fill_limits,
                                         fill_labels = tot_subs_fill_labels,
                                         land_sf = world_land,
                                         plot_labels = c("A) Median", "B) Mean", "C) Weighted Mean"),
                                         file_name = "subsidy_intensity_tot_grid_map",
                                         file_dir = results_dir,
                                         fill_palette = "seq")

@@

```{r, fig.width=4, fig.height=7}
# Total subsidies (region)
subsidy_intensity_tot_region_l <- MapMaker(data = subsidy_intensity_region,
                                         res = "region",
                                         x = "lon_bin_center",
                                         y = "lat_bin_center",
                                         fill = "tot_subs_KWh",
                                         fill_name = subs_fill_label,
                                         fill_breaks = tot_subs_fill_breaks,
                                         fill_limits = tot_subs_fill_limits,
                                         fill_labels = tot_subs_fill_labels,
                                         land_sf = world_land,
                                         region_sf = fao_regions,
                                         plot_labels = c("A) Median", "B) Mean", "C) Weighted Mean"),
                                         file_name = "subsidy_intensity_tot_region_map",
                                         file_dir = results_dir,
                                         fill_palette = "seq")

@@

# Total subsidies (grid)
subsidy_intensity_B_grid_l <- MapMaker(data = subsidy_intensity_binned,
                                         res = "grid",
                                         x = "lon_bin_center",
                                         y = "lat_bin_center",
                                         fill = "B_subs_KWh",
                                         fill_name = subs_fill_label,
                                         fill_breaks = B_subs_fill_breaks,
                                         fill_limits = B_subs_fill_limits,
                                         fill_labels = B_subs_fill_labels,
                                         land_sf = world_land,
                                         plot_labels = c("A) Median", "B) Mean", "C) Weighted Mean"),
                                         file_name = "subsidy_intensity_B_grid_map",
                                         file_dir = results_dir,
                                       fill_palette = "seq")

@@

```{r, fig.width=4, fig.height=7}
# Total subsidies (region)
subsidy_intensity_B_region_l <- MapMaker(data = subsidy_intensity_region,
                                         res = "region",
                                         x = "lon_bin_center",
                                         y = "lat_bin_center",
                                         fill = "B_subs_KWh",
                                         fill_name = subs_fill_label,
                                         fill_breaks = B_subs_fill_breaks,
                                         fill_limits = B_subs_fill_limits,
                                         fill_labels = B_subs_fill_labels,
                                         land_sf = world_land,
                                         region_sf = fao_regions,
                                         plot_labels = c("A) Median", "B) Mean", "C) Weighted Mean"),
                                         file_name = "subsidy_intensity_B_region_map",
                                         file_dir = results_dir,
                                         fill_palette = "seq")

@@

# Total subsidies (grid)
subsidy_intensity_BC_grid_l <- MapMaker(data = subsidy_intensity_binned,
                                         res = "grid",
                                         x = "lon_bin_center",
                                         y = "lat_bin_center",
                                         fill = "BC_subs_KWh",
                                         fill_name = subs_fill_label,
                                         fill_breaks = BC_subs_fill_breaks,
                                         fill_limits = BC_subs_fill_limits,
                                         fill_labels = BC_subs_fill_labels,
                                         land_sf = world_land,
                                         plot_labels = c("A) Median", "B) Mean", "C) Weighted Mean"),
                                         file_name = "subsidy_intensity_BC_grid_map",
                                         file_dir = results_dir,
                                        fill_palette = "seq")

@@

```{r, fig.width=4, fig.height=7}
# Total subsidies (region)
subsidy_intensity_BC_region_l <- MapMaker(data = subsidy_intensity_region,
                                         res = "region",
                                         x = "lon_bin_center",
                                         y = "lat_bin_center",
                                         fill = "BC_subs_KWh",
                                         fill_name = subs_fill_label,
                                         fill_breaks = BC_subs_fill_breaks,
                                         fill_limits = BC_subs_fill_limits,
                                         fill_labels = BC_subs_fill_labels,
                                         land_sf = world_land,
                                         region_sf = fao_regions,
                                         plot_labels = c("A) Median", "B) Mean", "C) Weighted Mean"),
                                         file_name = "subsidy_intensity_BC_region_map",
                                         file_dir = results_dir,
                                         fill_palette = "seq")

@@

```{r, fig.width=4, fig.height=7}
# Fmsy (region)
F_Fmsy_region_l <- MapMaker(data = upsides_region,
                            res = "region",
                            fill = "fv_fmsy",
                            fill_name = "F/Fmsy",
                            fill_breaks = seq(0,3, by = 0.75),
                            fill_limits = c(0, 3),
                            fill_labels = c("0", "0.75", "1.5", "2.25", "\u2265 3"),
                            land_sf = world_land,
                            region_sf = fao_regions,
                            plot_labels = c("A) Median", "B) Mean", "C) Weighted Mean"),
                            file_name = "F_Fmsy_region_map",
                            file_dir = results_dir,
                            fill_palette = "div",
                            fill_low = "#001f9e",
                            fill_high = "#EF3B2C",
                            fill_mid = "#ffffff",
                            fill_midpoint = 1)

@@

```{r, fig.width=4, fig.height=7}
# B/Bmsy (region)
B_Bmsy_region_l <- MapMaker(data = upsides_region,
                            res = "region",
                            fill = "bv_bmsy",
                            fill_name = "B/Bmsy",
                            fill_breaks = seq(0,2, by = 0.5),
                            fill_limits = c(0, 2),
                            fill_labels = c("0", "0.5", "1", "1.5", "\u2265 2"),
                            land_sf = world_land,
                            region_sf = fao_regions,
                            plot_labels = c("A) Median", "B) Mean", "C) Weighted Mean"),
                            file_name = "B_Bmsy_region_map",
                            file_dir = results_dir,
                            fill_palette = "div",
                            fill_low = "#0031f7",
                            fill_high = "#EF3B2C",
                            fill_mid = "#ffffff",
                            fill_midpoint = 1)

@@

```{r}
# Set some plot scales
subs_x <- c(0,4)
f_y <- c(0,3)
effort_fill_lim <- c(0,7.5e9)
effort_fill_breaks <- seq(0,7.5e9, length.out = 5)
effort_fill_labels <- format(seq(0,7.5e9, length.out = 5)/1e9, scientific = F, digits = 2)

@@

```{r}
w_mean_fuel_subs_vs_F_Fmsy_l <- MapMaker(data = subsidy_intensity_upsides_region,
                                        res = "corr",
                                        x = "fuel_subs_KWh_w_mean",
                                        x_name = paste0("Weighted Mean Subsidy Intensity ($/KWh)"),
                                        x_limits = c(0,1),
                                        y = "fv_fmsy",
                                        y_name = f_label,
                                        y_limits = f_y,
                                        fill = "fishing_KWh_lat_lon_sum",
                                        fill_name = effort_label,
                                        fill_limits = effort_fill_lim,
                                        fill_breaks = effort_fill_breaks,
                                        fill_labels = effort_fill_labels,
                                        file_name = "w_mean_fuel_subs_vs_F_Fmsy_plot",
                                        file_dir = results_dir)

@@

## Figure 1 (Using Bad Subisides)

```{r}
top_row <- plot_grid(

  plot_grid(subsidy_intensity_B_grid_l[["w_mean"]] + theme(legend.position = "none"),
            subsidy_intensity_B_region_l[["w_mean"]] + theme(legend.position = "none"),
            nrow = 1,
            label_x = 0,
            labels = c("A)", "B)")),

  get_legend(subsidy_intensity_B_grid_l[["w_mean"]]),

  ncol = 1,
  rel_heights = c(1, 0.2)

)

bottom_row <- plot_grid(
  F_Fmsy_region_l[["median"]],
  w_mean_B_subs_vs_F_Fmsy_l[["median"]] + theme(plot.margin = margin(1, 0, 1, 0, "cm")),
  nrow = 1,
  labels = c("C)", "D)")
)

Figure1 <- plot_grid(top_row,
                     bottom_row,
                     nrow = 2)

### 2020-03-26 scripts/01_data_wrangling.Rmd
and paper figures again

# Aggregate by ISCCAP groups and export for time series plot
fao_production_dat_edit_groups <- fao_production_dat_edit %>%
  group_by(iso3, year, isscaap_group, variable, units, source) %>%
  summarize(value = sum(value, na.rm = T))

>>>>

# Aggregate by ISCCAP groups and export for time series plot
fao_production_dat_edit_groups <- fao_production_dat_edit %>%
  group_by(iso3, year, fao_region = fishing_area, isscaap_group, variable, units, source) %>%
  summarize(value = sum(value, na.rm = T))
